Automated Topic Naming

### 2012-04-09 ese/ese.tex
minor spelling problem

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. 
Sometimes LDA produces topics that have a
very low association to documents, and in this paper we removed topics
that
exhibit very low document association. Our threshold for
topic inclusion was that a topic needed to be related to at least 1
document with a gamma (the variational
posterior Dirichlet~\cite{Blei2003} of a topic to a document, similar
to an association weight) of $1.0$ or greater.
The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N = 20$ was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

>>>>

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. 
Sometimes LDA produces topics that have a
very low association to documents, and in this paper we removed topics
that
exhibit very low document association. Our threshold for
topic inclusion was that a topic needed to be related to at least 1
document with a gamma (the variational
posterior Dirichlet~\cite{Blei2003} of a topic to a document, similar
to an association weight) of $1.0$ or greater.
The
PostgreSQL study was added later and we followed the same methodology
to extract topics from PostgreSQL, the choice of $N = 20$ was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.
